\documentclass[10pt, answers]{exam}

% loads all necessary packages (feel free to customize for your needs)

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{pifont}
\usepackage[english]{babel}
%\usepackage{fancyhdr}
%\pagestyle{fancy}
%\usepackage{totpages}
\usepackage[margin=0.8in]{geometry}
%\renewcommand{\headrulewidth}{0.0pt}
%\usepackage{framed}

%\ShortKey		% shows a short key answer sheet


\newcommand{\myversion}{} % this line is very important as it locates and allows the printed test to show the number of  the test (DONT DELETE IT)

% You probably want to change the next lines

\newcommand{\UniName}{Name of my University} 
\newcommand{\DeptName}{My Department} 
\newcommand{\ClassName}{My Class Name} 
\newcommand{\MyName}{Author: My name}
\newcommand{\ExamName}{Exam Name: Version \myversion}
\newcommand{\TermName}{Current Term}

\rfoot{Random test \# \myversion}

\begin{document}

\begin{center}
    \textbf{\Large \UniName} \\
    \textbf{\Large \DeptName} \vspace{0.5cm}  \\
    \textbf{\Large \ClassName} \\
	\textbf{\Large \MyName} \\
    \textbf{\Large \ExamName } \\
    \textbf{\Large \TermName}
 \end{center}

\vspace{1cm}
Name: \rule{4in}{.4pt}  \quad  \noindent Card:\enspace\hrulefill

%\rule[1ex]{\textwidth}{2pt}

\vspace{1cm}

\small

\begin{framed}

Instructions for this test:

\begin{itemize}

	\item Make sure you finish before the end of the exam time

	\item There is only one correct answer in all multiple choice questions

	\item Don't cheat!

\end{itemize}

\vspace{0.5cm}

{\large \emph{Good Luck!}}
\end{framed}

\begin{framed}
	Instructions on how to use RndTexExams (DELETE THIS IN THE FINAL VERSION)
	\begin{itemize}

		\item The switch statements for the text of the questions, including main text and answers are defined as @{Text for version 1}|{Text for version 2}@. For each question, fell free to define as many versions as needed.

		\item You can define the right answer in each version of the test by assigning the character [!] or [ver] in the right answer for version ver. See the rest of the file for examples.


	\end{itemize}

\end{framed}


\vspace{1cm}

\begin{questions}
	
\question 

	Which one is the correct answer in the next five alternatives?
	
	\begin{choices}
	\choice Choice 1
	\choice Choice 2
	\choice Choice 3
	\choice Choice 4
	\CorrectChoice Choice 5 - CORRECT
	\end{choices}
		
	
\question 
	
	Consider the following statements:
	
	\begin{enumerate}%[I]
		\item The color of the sky is generally @{blue}|{red}@		
		\item R has a @{high}|{low}@ number of packages for empirical research in Finance		
		\item Microsoft word is @{better}|{worse}@ than latex for creating structured documents
	\end{enumerate}
	
	Are correct:
	
	\begin{choices}	
	\choice [1] 1 and 2
	\choice 2 and 3
	\choice 1, 2 and 3
	\choice [2] Only 3
	\choice Only 1 
	\end{choices}	

\question 

	Which of the next answers do you think is the correct one? (there are three versions of this question. This is version @{1}|{2}|{3}@)
	
	\begin{choices}	
	\choice Choice 1 - Incorrect in all versions
	\choice [1] Choice 2 - @{Correct in version 1}|{Incorrect in version 2}|{Incorrect in version 3}@ 
	\choice [3] Choice 3 - @{Incorrect in version 1}|{Incorrect in version 2}|{Correct in version 3}@
	\choice Choice 4 - Incorrect in all versions
	\choice [2] Choice 5 - @{Incorrect in version 1}|{Correct in version 2}|{Incorrect in version 3}@
	\end{choices}	


\question 

	Consider the following statements:
	
	\begin{enumerate}%[I]
		\item Latex is @{good}|{bad}@ for structured documents
		
		\item Working with R and latex is a @{good}|{bad}@ choice for writing up and marking tests
		
		\item We @{love}|{hate}@ R
		
	\end{enumerate}
	
	Which statements are true?

	\begin{choices}
	\choice 1 e 2
	\choice [1] 1, 2 e 3
	\choice Only 3
	\choice 1 e 3
	\choice [2] None of the other options
	\end{choices}
	
\end{questions}

\end{document}
